New seismological constraints on the available parameter space of macroscopic dark matter

### 2016-08-21 Draft.tex
Update

\section{Seismic Wave Propagation}
The velocity of $p$-waves as a function of radius within the Earth and Moon (and presumably other spherical rocky celestial bodies) is of the form $v = a^2 - b^2 r^2$. Using Snell's law, we obtain the differential equations for the trajectory of $p$-wave rays within such bodies
\begin{align}
v^2 \notag&= \dot r^2 + \f{p_\te{ray}^2 v^4}{r^2}\,,\\
0 &=\dot\theta\pm\f{p_\te{ray} v^2}{r^2}\,.
\end{align}
where $r$ is the radial coordinate of the ray, $\theta$ is the polar angle of the ray measured from the center of the body, and $p_\te{ray}$ is the ray constant, whose value is fixed along a ray trajectory. These equations can be integrated. In the case that $v = a^2 - b^2 r^2$, we obtain for some constants $q$ and $\theta_0$.
\begin{align}
\notag&r(t) = \f{a\sqrt{(q^2e^{2abt}-b)^2 + 4a^2b^4 p_\te{ray}}}{b\sqrt{(qe^{2abt}+b)^2 + 4a^2b^4 p_\te{ray}}}\,,\\
&\tan(\theta(t) - \theta_0) = \f{qe^{4abt}-b^2}{4ab^3p_\te{ray}}+abp_\te{ray}\,.
\end{align}
\textit{A priori} these are geodesics on the Poincar\'e disc of radius $\f ab$ based on the form of $v$.

@@

This procedure is repeated for 17 values of $D$ spaced evenly by $100\,\te{km}$. The average fraction of detectable surface area is then
\begin{align}
\scr F = \sum_D\f{\scr F_D D}{D}\,.
\end{align}
If there are $n$ lunar seismometers, suppose each occupies its own HEALPix pixel. Then $\scr N = n/12\times 2^{n_\te{side}}$ is the fraction of the moon which could potentially measure a signal. The likelihood of detection is then
\begin{align}
\scr P = 1-(1-\scr F)(1-\scr N)\,.
\end{align}
If $\scr M$ Macros impact the moon, the likelihood of any of them being detected is
\begin{align}
{\cal P} = 1-(1-\scr P)^\scr{M} = 1-\ps{(1-\scr F)(1-\scr N)}^\scr M\,.
\end{align}

>>>>

\section{Seismic Wave Propagation}
The velocity of $p$-waves as a function of radius within the Earth and Moon (and presumably other spherical rocky celestial bodies) is of the form $v = a^2 - b^2 r^2$. Using Snell's law, we obtain the differential equations for the trajectory of $p$-wave rays within such bodies
\begin{align}
v^2 \notag&= \dot r^2 + \f{p_\te{ray}^2 v^4}{r^2}\,,\\
0 &=\dot\theta\pm\f{p_\te{ray} v^2}{r^2}\,.
\end{align}
where $r$ is the radial coordinate of the ray, $\theta$ is the polar angle of the ray measured from the center of the body, and $p_\te{ray}$ is the ray parameter, whose value is fixed along a ray trajectory. These equations can be integrated. In the case that $v = a^2 - b^2 r^2$, we obtain for some constants $q$ and $\theta_0$.
\begin{align}
\notag&r(t) = \f{a\sqrt{(q^2e^{2abt}-b)^2 + 4a^2b^4 p_\te{ray}}}{b\sqrt{(qe^{2abt}+b)^2 + 4a^2b^4 p_\te{ray}}}\,,\\
&\tan(\theta(t) - \theta_0) = \f{qe^{4abt}-b^2}{4ab^3p_\te{ray}}+abp_\te{ray}\,.
\end{align}
\textit{A priori} these are geodesics on the Poincar\'e disc of radius $\f ab$ based on the form of $v$.

@@

This procedure is repeated for 17 values of $D$ spaced evenly by $100\,\te{km}$. The average fraction of detectable surface area is then
\begin{align}
\scr F = \sum_D\f{\scr F_D D}{D}\,.
\end{align}
If there are $n$ lunar seismometers, suppose each occupies its own HEALPix pixel. Then $\scr N = n/12\times 2^{n_\te{side}}$ is the fraction of the moon which could potentially measure a signal. If $\scr M$ Macros impact the moon, the likelihood of any of them being detected is
\begin{align}
\scr P = 1-\ps{(1-\scr F)(1-\scr N)}^\scr M\,.
\end{align}
